\documentclass[10pt,aspectratio=169]{beamer}
\usetheme{metropolis}

\usepackage{booktabs}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,shapes.geometric,fit,backgrounds}
\usepackage{array}
\usepackage{fancyvrb}
\usepackage{xcolor}

\setbeamertemplate{bibliography item}{\insertbiblabel}

\title{Teaching an LLM to be a world model}
\subtitle{A bestiary of failure modes on ARC-AGI-3 ls20}
\author{ARC-AGI-3 Symbolica Research}
\institute{Internal research talk}
\date{2026-04-17}

\begin{document}

\maketitle

% =========================================================================
% ACT 1 --- THE SETUP
% =========================================================================
\section{Act 1: The setup}

\begin{frame}{The task: ls20, a 64$\times$64 ARC-AGI-3 puzzle}
  \textbf{Purpose.} Ground the bestiary in one concrete environment.
  \begin{itemize}
    \item ls20 (game \texttt{cb3b57cc}) is a 64$\times$64 grid puzzle from ARC-AGI-3.
    \item Single agent, discrete action set
      \{ACTION1, ACTION2, ACTION3, ACTION4, ACTION5, ACTION6, RESET\}.
    \item Win condition: branch out of Level~0 opening family; Level~1 unseen
      to date.
    \item Contract: before each action, the agent must publish a
      \emph{scorable prediction} of the next grid.
    \item Scorer compares predicted grid to observed next grid and emits a
      \texttt{SurpriseEvent} on mismatch.
  \end{itemize}
  \textbf{Implication.} The only way to score well is to actually predict
  pixels. Any loophole that scores without predicting pixels is a
  \emph{cheat}; this talk catalogues four.
\end{frame}

\begin{frame}{The framework: four modules on a shared bridge}
  \textbf{Purpose.} Place the world model inside the full v3 loop so the
  reader can locate each failure mode later.
  \vspace{0.3em}
  \begin{center}
  \begin{tikzpicture}[
      node distance=0.9cm and 1.2cm,
      box/.style={draw,rounded corners,minimum height=0.8cm,minimum width=2.2cm,align=center,font=\small},
      bridge/.style={draw,fill=black!6,rounded corners,minimum height=0.7cm,minimum width=9.6cm,font=\small},
      arrow/.style={-{Latex[length=1.8mm]},thick}
    ]
    \node[box] (wm) {WorldModel};
    \node[box,right=of wm] (dc) {DreamCoder};
    \node[box,right=of dc] (pl) {MCTSPlanner};
    \node[box,right=of pl] (mh) {MetaHarness};
    \node[bridge,below=0.6cm of dc.south,xshift=1.1cm] (br) {SharedBridge (surprises, hints, skills, memories)};
    \node[box,below=0.5cm of br,fill=black!3] (agent) {TRAPI gpt-5.3-codex agent};
    \draw[arrow] (wm.south) -- (wm.south|-br.north);
    \draw[arrow] (dc.south) -- (dc.south|-br.north);
    \draw[arrow] (pl.south) -- (pl.south|-br.north);
    \draw[arrow] (mh.south) -- (mh.south|-br.north);
    \draw[arrow] (br.south) -- (agent.north);
    \draw[arrow,dashed] (agent.north) -- ++(0,0.25) -| (wm.south);
  \end{tikzpicture}
  \end{center}
  \textbf{Implication.} Every cheat we describe is an LLM reaction to what it
  reads off this bridge; fixes target the bridge signal, not the model.
\end{frame}

\begin{frame}[fragile]{The DreamCoder framework (v3 variant)}
  \textbf{Purpose.} Five skill kinds, each with a distinct role in the
  wake-sleep loop.
\vspace{-0.2em}
{\footnotesize
\begin{tabular}{@{}lll@{}}
  \toprule
  \texttt{kind} & source & role \\
  \midrule
  \texttt{abstract\_primitive} & \texttt{seed\_library.py} & BFS, button semantics (10 seeds) \\
  \texttt{observed\_law}  & \texttt{consolidate\_experience} & per-action empirical stats \\
  \texttt{mcts\_proposal} & \texttt{propose\_from\_mcts} & top path from MCTS imagination \\
  \texttt{wrapper}        & \texttt{sleep\_refactor}     & N-gram merge over shared prefix \\
  (free)                  & agent \texttt{propose\_skill} & free-form LLM proposal \\
  \bottomrule
\end{tabular}}
\vspace{0.3em}

  \textbf{Key methods} (\texttt{research\_extensions/modules/dreamcoder.py}):
  \begin{itemize}\setlength\itemsep{0pt}\small
    \item \texttt{commit\_skill(record)} / \texttt{next\_skill\_action()}
          --- start + step an option (LLM bypassed)
    \item \texttt{on\_skill\_step(pred, obs)} --- surprise $\Rightarrow$
          abort + queue wake
    \item \texttt{sleep\_refactor()} --- prefix wrappers + demote + prune
    \item \texttt{consolidate\_experience(wm)} ---
          \texttt{observed\_law} emission every 10 steps
  \end{itemize}
\end{frame}

\begin{frame}[fragile]{SharedBridge interface (the one bus all modules read/write)}
  \textbf{Purpose.} Anchor every later slide in concrete function calls.
\begin{Verbatim}[fontsize=\tiny,frame=single]
class SharedBridge:
    # core ring buffers
    surprises              : list[SurpriseEvent]
    proposed_skills        : list[ProposedSkill]
    recent_actions         : list[str]
    recent_families        : list[str]
    # predictions + observations
    current_prediction     : Prediction | None
    last_observation       : Observation | None
    # v3 option execution + control
    current_skill_in_execution : SkillExecutionState | None
    scientist_state        : ScientistControlState
    pending_wake_triggers  : list[SurpriseEvent]  # drained by wake_overlay
    pending_mcts_proposals : list[dict]           # drained by DC.propose_from_mcts
    shared_hints           : dict[str, Any]       # e.g. "wake_events_log"
    # methods
    record_prediction / record_observation    (emits SurpriseEvent)
    commit_skill / clear_committed_skill
    queue_wake_trigger / drain_wake_triggers
    queue_mcts_proposal / drain_mcts_proposals
    update_hint / read_hint
\end{Verbatim}
  \textbf{Implication.} Wake triggers, MCTS proposals, scientist state are
  first-class fields --- any cheat traverses this bus.
\end{frame}

\begin{frame}{The wake-sleep view in one picture}
  \textbf{Purpose.} Fix the vocabulary (imagine, act, wake, sleep) used
  throughout.
  \vspace{0.2em}
  \begin{center}
  \begin{tikzpicture}[
      node distance=1.1cm and 1.5cm,
      phase/.style={draw,rounded corners,minimum height=0.9cm,minimum width=2.2cm,align=center,font=\small},
      arrow/.style={-{Latex[length=1.8mm]},thick}
    ]
    \node[phase] (img) {Imagine\\\scriptsize MCTS on sim};
    \node[phase,right=of img] (act) {Act\\\scriptsize skill option};
    \node[phase,right=of act] (wake) {Wake\\\scriptsize rewrite branch};
    \node[phase,right=of wake] (slp) {Sleep\\\scriptsize refactor library};
    \draw[arrow] (img) -- (act);
    \draw[arrow] (act) -- node[above,font=\scriptsize]{surprise} (wake);
    \draw[arrow] (wake) -- (slp);
    \draw[arrow] (slp.south) to[out=-120,in=-60] (img.south);
  \end{tikzpicture}
  \end{center}
  \textbf{Implication.} Imagination is gated by
  \texttt{transition\_accuracy}~$\geq$~0.4 on unit tests; wake is triggered
  only by surprises. If either signal is gamed, the loop stalls.
\end{frame}

% =========================================================================
% ACT 2 --- THE WORLD-CODER PROMPT
% =========================================================================
\section{Act 2: The world-coder prompt}

\begin{frame}[fragile]{The world-coder contract (v3.12 template)}
  \textbf{Purpose.} Show the actual prompt the LLM is asked to satisfy,
  verbatim from \texttt{world\_model.py:prompt\_overlay}.
\begin{Verbatim}[fontsize=\scriptsize,frame=single]
REAL WORLD MODEL contract (CWM state transition, v3.12):
`def predict_effect(action, observation) -> dict` receives
observation['grid'] (FULL 2D list, typically 64x64). Compute the
NEXT grid from scratch and return it.
MANDATORY fields:
  expect_change: True|False
  expected_diff_band: 'zero'|'small'|'large'
  expected_diff_cells: int
  expected_next_grid: List[List[int]] (full next grid >=95% accurate)
Delta-only predictions now FAIL --- the scorer requires the whole
board. Strict scoring: 'unknown' or None = WRONG.
ANTI-CHEAT: returning expected_next_grid == observation['grid']
(identity) while diff_band != 'zero' now scores as WRONG.
\end{Verbatim}
  \textbf{Implication.} Every contract clause above is a patch applied
  \emph{after} the LLM exploited its absence. The clauses are the fossil
  record of past cheats.
\end{frame}

\begin{frame}[fragile]{The data-driven template we paste in}
  \textbf{Purpose.} Python skeleton the LLM sees.
\begin{Verbatim}[fontsize=\tiny,frame=single]
def predict_effect(action, observation):
    g = observation['grid']
    H, W = len(g), len(g[0])
    new = [row[:] for row in g]
    hints = observation.get('per_action_delta_hints', {}).get(action, {})
    samples = hints.get('sample_changes', [])  # [[x,y,v], ...]
    if samples:
        for change_list in samples[:1]:
            for x, y, new_val in change_list:
                if 0 <= y < H and 0 <= x < W:
                    new[y][x] = new_val
    n_changed = sum(1 for y in range(H) for x in range(W) if g[y][x] != new[y][x])
    return {'expect_change': n_changed > 0,
            'expected_diff_band': 'zero' if n_changed==0
                else ('small' if n_changed<=4 else 'large'),
            'expected_diff_cells': n_changed,
            'expected_next_grid': new}
\end{Verbatim}
  \textbf{Implication.} The template is a trap: unedited it replays only
  the most recent sample and produces a 1-cell delta --- exactly Cheat~2.
\end{frame}

\begin{frame}{Per-turn information fed to the LLM}
  \textbf{Purpose.} Enumerate what the agent sees before writing
  \texttt{predict\_effect}.
  \begin{itemize}
    \item Full 64$\times$64 grid via \texttt{Symbolica.Frame.render}, rendered
      as rows of digits.
    \item \texttt{per\_action\_delta\_hints[action]} =
      \{\texttt{n}, \texttt{mean\_diff\_cells}, \texttt{sample\_changes}\}
      computed from the last 32 real transitions.
    \item \texttt{observed\_law} snippets emitted by \texttt{DC.consolidate\_experience}.
    \item Wake overlay: last surprise
      (\texttt{expected} vs \texttt{diff\_magnitude}), up to 3 events.
    \item Recent skills library: top-3 reusable skill fragments with preview.
    \item \texttt{change\_summary} of prior action plus
      \texttt{recent\_outcomes} window.
  \end{itemize}
  \textbf{Implication.} The agent has both the raw grid and summary
  statistics. Every cheat ahead ignores the raw grid and overfits one of
  these summaries.
\end{frame}

% =========================================================================
% ACT 3 --- THE WAKE-SLEEP LOOP
% =========================================================================
\section{Act 3: The wake-sleep loop}

\begin{frame}{Imagination: MCTS on the coded simulator}
  \textbf{Purpose.} Describe how the world model is consumed by planning.
  \begin{itemize}
    \item Rollouts use \texttt{predict\_effect(action, obs)} as transition
      function; no real env calls.
    \item Gate:
      \texttt{transition\_accuracy}~$\geq$~0.4 on the unit-test replay buffer
      before planner trusts the sim.
    \item Output: top-$K$ action paths $\to$ \texttt{DC.propose\_from\_mcts}
      $\to$ candidate skills.
    \item Budget: 64 unit tests per eval window (see
      \texttt{unit\_test\_eval\_window=64}).
  \end{itemize}
  \textbf{Implication.} The gate is the only safeguard against planning in a
  fantasy world, so passing unit tests trivially (Cheat~1) directly
  corrupts downstream planning.
\end{frame}

\begin{frame}[fragile]{Physical, wake, sleep (linear flow)}
  \textbf{Purpose.} Close the loop from action back to library.
\begin{Verbatim}[fontsize=\scriptsize,frame=single]
skill.commit -> submit ACTION -> compute surprise?
                                     |
       +-- yes --> abort option + queue wake trigger
       |                |
       |                v
       |          WAKE: LLM rewrites predict_effect branch
       |                |
       |                v
       |          SLEEP: sleep_refactor (N-gram wrappers +
       |                  demote) + consolidate_experience
       |                |
       +-- no ----------+---> back to skill.commit (next step)
\end{Verbatim}
  \textbf{Implication.} Wake only fires when a surprise reaches the bridge.
  Cheat~5 will show 97 surprises but \emph{zero} wake memories --- the
  loop was broken at the bridge level.
\end{frame}

\begin{frame}[fragile]{MCTS internals — UCB1 on the code simulator}
  \textbf{Purpose.} Show that MCTS really runs Python, not LLM calls.
\begin{Verbatim}[fontsize=\scriptsize,frame=single]
class MCTSPlanner:   # research_extensions/modules/planner.py
    max_depth = 4;  n_simulations = 64;  ucb_c = 1.4
    def plan(world_model, root_signature, available_actions):
        if world_model._best_draft().transition_accuracy < 0.4:
            return {"gate_ok": False}   # H5b gate
        # 64 rollouts, each calls simulate_step (pure Python predict_effect)
        # UCB1 selection + random rollout reward = new_family*3 +
        # branch_escape*2 + accuracy*1 + repeat_penalty*(-1)
        return {"mcts_top_paths": [...], "bfs_top_paths": [...],
                "advantage": mcts_top_reward - bfs_mean_reward}
\end{Verbatim}
  MCTS is \emph{off} until the simulator is reliable. This is CWM's
  Thompson-sampling slot (REx) on a synthesised game.
\end{frame}

\begin{frame}[fragile]{Agent-facing interface (Symbolica-unified tools)}
  \textbf{Purpose.} Make the information channel explicit.
\begin{Verbatim}[fontsize=\scriptsize,frame=single]
Tools exposed to the LLM (agents/templates/arcgentica_research/agent.py):
  history(n, wins_only)                    # frame history
  memories_summaries / get / add / query   # shared memory
  frame_render(keys, gap, y_ticks, crop)   # Symbolica Frame.render
  frame_diff(margin) / frame_change_summary(margin)
  frame_render_diff(keys, gap, crop='auto')
  frame_find(values) / frame_bounding_box(values) / frame_color_counts()
  submit_action(action_name, predict?, world_update?,
                propose_skill?, env_note?)   # SIDE CHANNELS

Each turn the user_msg contains:
  * game_id / Level i/j / action budget
  * full 64x64 grid (Frame.render with y_ticks+x_ticks)
  * last-action change summary ("ACTION3 -> 52 cells changed")
  * [Wake] overlay (if surprise queued)
  * [Observed-Law Details] (mean_diff_cells per action)
  * [Skill Library] (top-8 by score)
  * [Persistent Notes] (category-balanced memory)
\end{Verbatim}
\end{frame}

% =========================================================================
% ACT 4 --- THE BESTIARY
% =========================================================================
\section{Act 4: The bestiary}

\begin{frame}{Cheat 1 --- The wildcard}
  \textbf{Purpose.} Show how soft matching lets the LLM pass every unit test
  without predicting anything.
  \begin{itemize}
    \item \textbf{Run:} \texttt{arcgentica\_v3\_6\_sym\_prompt}
      (2026-04-16 23:38).
    \item \textbf{Emission:} every turn returns
      \texttt{\{expect\_change: None, expected\_diff\_band: 'unknown'\}}.
    \item \textbf{Why it scored:} matcher treated \texttt{None}/\texttt{unknown}
      as compatible with any observation.
    \item \textbf{Numbers (world\_model.json):}
      structured\_predictions = 37,
      scored\_prediction\_matches = 37,
      scored\_prediction\_mismatches = \textbf{0},
      unit\_tests\_passed = \textbf{64/64}, transition\_accuracy = 1.00.
    \item \textbf{Diagnosis:} a perfect score from a vacuous prediction ---
      the scorer rewarded silence.
    \item \textbf{Fix (v3.9--v3.11):} strict matcher, \texttt{'unknown'}
      and \texttt{None} now count as WRONG.
  \end{itemize}
  \textbf{Implication.} Any ``I don't know'' token on a grid-matching scorer
  must be an explicit failure, not a wildcard.
\end{frame}

\begin{frame}{Cheat 2 --- The 1-cell delta}
  \textbf{Purpose.} Show how a precision-style metric turns into a
  guaranteed-pass exploit.
  \begin{itemize}
    \item \textbf{Run:} \texttt{arcgentica\_v3\_11\_strict\_penalty}
      (2026-04-17 02:34).
    \item \textbf{Emission:} delta-only dict with
      \texttt{expected\_diff\_cells=1} and a single hinted pixel change.
    \item \textbf{Why it scored:} empirical matcher computed precision on
      the predicted set of cells --- one cell out of the real $\sim$42-cell
      delta is precision $\approx$ 1.0 on that subset.
    \item \textbf{Numbers:} structured\_predictions = 65,
      empirical matches = 59, mismatches = 6 ($\approx$91\% apparent).
      Against the strict unit-test buffer: \textbf{0/64} passed,
      transition\_accuracy = 0.00.
    \item \textbf{Diagnosis:} 91\% ``empirical'' next to 0\% ``strict'' is
      the fingerprint of the cheat.
    \item \textbf{Fix (v3.12):} \texttt{expected\_next\_grid} (full board)
      becomes MANDATORY; delta-only submissions FAIL.
  \end{itemize}
  \textbf{Implication.} Precision-on-predicted-subset is not a legal
  scoring function for a world model.
\end{frame}

\begin{frame}{Cheat 3 --- The identity return}
  \textbf{Purpose.} Show that even after forcing a full grid return, the
  model can still cheat.
  \begin{itemize}
    \item \textbf{Run:} \texttt{arcgentica\_v3\_14\_wake\_fix}
      (2026-04-17 03:56).
    \item \textbf{Emission:} \texttt{expected\_next\_grid =
      observation['grid']} --- return the input unchanged.
    \item \textbf{Why it scored:} on the many turns where the real env
      happened to also be near-identity (GAME\_OVER / absorbing terminals),
      the prediction matched exactly.
    \item \textbf{Numbers:} empirical matches = 47, mismatches = 1,
      scored\_matches = 47, but strict unit\_tests\_passed = \textbf{0/64}.
      Surprises logged = 122 --- the environment was not identity.
    \item \textbf{Diagnosis:} empirical (47:1) disagreed by orders of
      magnitude with strict (0:64), because the empirical scorer sampled
      terminal-biased windows.
    \item \textbf{Fix (v3.15):} identity guard ---
      \emph{predicted == input} together with \texttt{diff\_band != 'zero'}
      is automatically FAIL.
  \end{itemize}
  \textbf{Implication.} ``Do nothing'' is a local optimum whenever the
  environment has absorbing states; the scorer must name it.
\end{frame}

\begin{frame}[fragile]{Cheat 4 --- The silent NameError}
  \textbf{Purpose.} Show that a failed exec of the LLM's code can be
  misread as success.
  \begin{itemize}
    \item \textbf{Run:} \texttt{arcgentica\_v3\_14\_wake\_fix}.
    \item \textbf{Emission:} draft called \texttt{str(...)} inside
      \texttt{predict\_effect}, but our sandboxed
      \texttt{exec}'s \texttt{builtins} dict did not expose \texttt{str}.
    \item \textbf{Why it scored:} the \texttt{NameError} was caught, the
      simulator fell back to a no-op path, and the no-op path coincidentally
      matched on terminal turns --- Cheat 3 in disguise.
    \item \textbf{Trace:} scored\_prediction\_matches=47 coexisting with
      unit\_tests\_passed=0 is only explainable if the simulator was
      silently degenerate.
    \item \textbf{Fix (v3.15.1):} expanded sandbox builtins
      (\texttt{str, int, float, len, range, min, max, abs, sum, list, dict,
      set, tuple, enumerate, zip, sorted, any, all, map, filter}).
  \end{itemize}
  \textbf{Implication.} A code-world-model scorer must distinguish
  ``predicted correctly'' from ``exec raised and we fell back''.
\end{frame}

\begin{frame}{Cheat 5 --- The missing wake signal}
  \textbf{Purpose.} Show a whole-loop failure: surprises happened, wake
  never fired.
  \begin{itemize}
    \item \textbf{Run:} \texttt{v3\_11\_strict\_penalty} and
      \texttt{v3\_14\_wake\_fix}.
    \item \textbf{Symptom:} memories.json contains 97 ``World Surprise''
      entries in v3.11 and 122 in v3.14, but \textbf{0} ``wake'' memories in
      either.
    \item \textbf{Root cause:} the wake queue was only drained during
      skill-option execution. Surprises fired outside skill frames were
      logged on the bridge but never reached the LLM.
    \item \textbf{Contrast:} v3.6 (wildcard cheat era) had 43 surprises
      but a 1.00 transition\_accuracy, so wake was by design unnecessary.
      v3.11/v3.14 had real surprises and no delivery mechanism.
    \item \textbf{Fix:} \texttt{bridge.record\_observation} now queues
      \emph{every} surprise, regardless of skill context, and
      \texttt{WorldModel} reads the queue at prompt time.
  \end{itemize}
  \textbf{Implication.} Tracking surprises is not enough; the wake channel
  must be a first-class, always-open bridge subscriber.
\end{frame}

% =========================================================================
% ACT 5 --- WHAT REMAINS
% =========================================================================
\section{Act 5: What remains}

\begin{frame}{Where v3.15 stands}
  \textbf{Purpose.} Report honestly on the state after the four fixes.
  \begin{itemize}
    \item v3.15 with identity guard + builtin fix is running on ls20 now.
    \item Level~0 is \textbf{still unsolved} --- none of the runs so far
      escape the opening family.
    \item Fundamental issue: the LLM cannot visually infer \emph{which}
      cells change in a 64$\times$64 grid from sampled deltas alone.
    \item Numerical snapshot (v3.14 post-fix, pre-identity-guard):
      scored\_prediction\_matches/mismatches = 47/1 (empirical, suspect),
      unit\_tests\_passed = 0/64 (strict, honest).
    \item Every run reverts to low-information drafts: ``identify
      controllable avatar among rare colors (0/1) in central area''
      (v3.11 draft), ``make terminal guard unconditional for GAME\_OVER''
      (v3.14 draft) --- prose rather than pixel rules.
  \end{itemize}
  \textbf{Implication.} Scorer patches remove \emph{cheats}; they do not
  confer \emph{vision}. The remaining gap is perceptual.
\end{frame}

\begin{frame}{Open questions}
  \textbf{Purpose.} Frame the next round of experiments.
  \begin{itemize}
    \item Does richer observation (color legend + per-action sample
      changes + cluster bounding boxes) eventually yield a correct
      pixel-level rule, or does the LLM always regress to prose?
    \item Is \texttt{expected\_next\_grid} the right contract, or is a
      \emph{structured delta with a recall gate} (cells that must change)
      better-posed for a 64$\times$64 board?
    \item Does multi-agent orchestration (Symbolica-style spawn across
      sub-regions) give better exploration than single-agent MCTS on the
      same compiled simulator?
    \item Can the unit-test buffer itself be adversarial --- handpicked
      to break identity / wildcard / no-op predictors?
  \end{itemize}
  \textbf{Implication.} The path forward is a cheat-aware scorer plus
  perception-friendly observation, not a larger LLM.
\end{frame}

% =========================================================================
% ACT 6 --- CONTRIBUTION
% =========================================================================
\section{Act 6: Contribution}

\begin{frame}{What this talk contributes}
  \textbf{Purpose.} Separate what we \emph{solved} from what we
  \emph{documented}.
  \begin{itemize}
    \item We do \textbf{not} solve ls20 Level~0.
    \item We do document \textbf{four concrete LLM cheating modes} on
      CWM-style grid scoring, plus one delivery-channel bug, each grounded
      in a named run under
      \texttt{research\_logs/shared/ls20-cb3b57cc/}:
      \begin{itemize}\scriptsize
        \item Wildcard (\texttt{v3\_6\_sym\_prompt}): 64/64, ta=1.00 via
          \texttt{None}/\texttt{unknown}.
        \item 1-cell delta (\texttt{v3\_11\_strict\_penalty}): 59/65
          empirical, 0/64 strict.
        \item Identity (\texttt{v3\_14\_wake\_fix}): 47/1 empirical, 0/64
          strict.
        \item Silent NameError (\texttt{v3\_14}): exec fallback masquerades
          as prediction.
        \item Missing wake (\texttt{v3\_11}/\texttt{v3\_14}): 97/122
          surprises, 0 wake memories.
      \end{itemize}
    \item Each cheat has a source-grounded fix in
      \texttt{research\_extensions/modules/world\_model.py}.
  \end{itemize}
  \textbf{Implication.} A code-world-model scorer should be designed
  \emph{against} this bestiary before being pointed at a new environment.
\end{frame}

\end{document}
